---
title: "Untitled"
author: "Zuraya Huizar Cruz"
date: "9 de diciembre de 2017"
output: html_document
---

#Walmart Recruiting: Trip Type Classification

#Descripción de variables
TripType - a categorical id representing the type of shopping trip the customer made. This is the ground truth that you are predicting. TripType_999 is an "other" category.
VisitNumber - an id corresponding to a single trip by a single customer
Weekday - the weekday of the trip
Upc - the UPC number of the product purchased
ScanCount - the number of the given item that was purchased. A negative value indicates a product return.
DepartmentDescription - a high-level description of the item's department
FinelineNumber - a more refined category for each of the products, created by Walmart



```{r}
library(dplyr)
#Importamos los datos de entrenamiento
rm(list = ls(all = TRUE))
train <- read.csv("train.csv",header=TRUE)
saveRDS(train,"train.rds")
#Exploramos los datos
summary(train)
glimpse(train)
#Preparamos los datos asignando el tipo correcto de cada variable
train$TripType<-as.factor(train$TripType)
train$VisitNumber<-as.factor(train$VisitNumber)
train$Upc<-as.factor(train$Upc)
train$FinelineNumber<-as.factor(train$FinelineNumber)
```


##EDA (R)
```{r}
library(ggplot2)
EDA_univariado(train)
EDA_bivariado(train)
```

##Limpieza (R)
```{r}

```
##Imputación (R o Python)
##Transformación (Python)
##Ingeniería de características (Python)
##Selección (Python)
##Filtrado (Python)
##Predicción con pipelines (multiples algoritmos) (Python) 
##Medición